Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-05-24 extended_catalog/paper/extended_catalog.tex
modifying plots & fixing legend

\usepackage{rotating}
\usepackage{amsmath}
\usepackage{graphicx}

\newcommand{\mev}{\text{MeV}}
\newcommand{\gev}{\text{GeV}}
\newcommand{\sr}{\text{sr}}
\newcommand{\cm}{\text{cm}}
\newcommand{\tsext}{\ensuremath{\text{TS}_\text{ext}}}
\newcommand{\ts}{\text{TS}}
\newcommand{\pointlike}{{\em pointlike}}
\newcommand{\gtlike}{{\em gtlike}}

@@

On the other hand, since the null hypothesis rests on the edge of
parameter space, when the extension is fixed to 0, Wilk's Theorem does
not formally hold\cite{Warnings about Wilk's Theorem Paper}.  One might
expect the actual distribution to be a half $\chi^2_1$ distribution with
one degree of freedom plus half of a delta function at 0:
\begin{equation}
  P(\ts)=\tfrac{1}{2}(\chi^2_1(\text{TS})+\delta(\text{TS})).
\end{equation}
The false detection probability can be estimated by integrating this function 
from an observed test statistic value to infinity. It is for this
particular distribution that the often quoted result holds that
$\sqrt{\ts}$ is a measure of the number of $\sigma$ of the detection.

@@

\section{Monte Carlo Validation}

@@

Fermi LAT data was simulated using the publically avaliabable Science
Tools package {\em gtobssim}\cite{GTOBSSIM_CITATION}. The sources were
simulated with a powerlaw spectral model with 6 Were given 6 $>100\mev$
fluxes ranging from $3\times 10^{-9} \text{ph}/\text{cm}^2/\text{s}$ to 
$10^{-6} \text{ph}/\text{cm}^2/\text{s}$.
The sources were then simulated with spectral index ($\gamma$) values of
1.5, 2, 2.5, and 3.  These values were picked to probe a representative
range measurable values.  For particular spectral indices, only the
fluxes which would create a statistically significant source detection
($\ts>25$) where selected, since we are only interested in
testing for extension sources with a significant extent. The sources were
simulated on top of an isotropic powerlaw background with a Sreekumar-like
spectrum ($>100\mev$ flux of 1.5e-5 and spectral index 2.1).\cite{Sreekumar
et al. ApJ 494 pag 523 1998}

The monte carlo simulation was perforormed over a one year time interval using
a default rocking profile and an assumed livetime fraction of 0.8.
The reconstruction was perfromed with events from an energy range of
$1\gev$ to $100\gev$ using 4 energy bins per decade and using the Pass 7 Version 6
source IRFs to be consistent with the following analysis.

@@

To calculate the LAT's sensitivity to spatially extended sources,
we simulated sources with a uniform radially symmetric
disk morphology on top of a powerlaw
Sreekumar-like isotropic spectrum.\cite{Sreekumar et al. ApJ 494 pag
523 1998}.  For a given extension and spectral index, we calculated the
sensitivity by varying the flux of a source until we found 
when $\tsext=25$. In particular, we hand picked a flux range
where $\tsext<25$ and $\tsext>25$ and simulated 10 points with
a log uniform distribution in this range and performed an extension
test for each of these fluxes. Since the measured signifciance is
a statistical which will vary from realization to realization,
we then repeated this procedure >15 times for each realization.
By fitting a line to the flux vs $\tsext$ data, we were able to
estimage the flux at which $\tsext=25$.

@@

First, we took the spatial and spectral model found using \pointlike
and performed a crosscheck by refitting the spectral parameters using 
\gtlike.
We used a square ROI $10^\circ$ in diamater, the same 4 degrees
per decade, and $0.125^\circ$ energy binning.
The \gtlike analysis provided a second estimate of the spectral
paramters of the extended source as well as a second calculation of
$\text{TS}_\text{disk}$, $\text{TS}_\text{point}$, and 
$\tsext$. We only looked for extended sources which 
both \pointlike and \gtlike considered significantly extended.

@@

A furthere test we did to validate our analysis was to test all of the

@@

\begin{table}
  \begin{centering}
\begin{tabular}{ | r | r | r | r | }
\hline
$\gamma$ & flux ($\text{ph}/\text{cm}^2/\text{s}$) & $N_\text{sims}$ & $<\text{TS}>$ \\
\hline
  1.5 &          $10^{-6}$ &           11405 &  90861 \\
      &  $3\times 10^{-7}$ &           11490 &  21922 \\
      &          $10^{-7}$ &           11101 &   5765 \\
      &  $3\times 10^{-8}$ &           10269 &   1262 \\
      &          $10^{-8}$ &            9941 &    306 \\
      &  $3\times 10^{-9}$ &           10427 &     61 \\
\hline
    2 &          $10^{-6}$ &           11632 &  22025 \\
      &  $3\times 10^{-7}$ &           11622 &   4886 \\
      &          $10^{-7}$ &           11115 &   1159 \\
      &  $3\times 10^{-8}$ &           10503 &    222 \\
      &          $10^{-8}$ &            9893 &     50 \\
\hline
  2.5 &          $10^{-6}$ &           11522 &   4722 \\
      &  $3\times 10^{-7}$ &           11445 &    948 \\
      &          $10^{-7}$ &           10966 &    202 \\
      &  $3\times 10^{-8}$ &            8227 &     41 \\
\hline                                                
    3 &          $10^{-6}$ &           11264 &    949 \\
      &  $3\times 10^{-7}$ &           10986 &    172 \\
      &          $10^{-7}$ &            7855 &     40 \\
\hline
\end{tabular}
\caption{List of the spectral models used in the monte carlo simulation of
\pointlike. $N_\text{sims}$ is the number of monte carlo simluations
which produce a significant source detection.The final column is the
average test statistic that was found during the monte carlo fit of
the source. Only simluations which were deemed significant ($\text{TS}>25$)
were kept.}
\label{ts_ext_num_sims}
  \end{centering}
\end{table}

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/ts_ext_emin_1000.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v3/plot.py
    % using data from /nfs/slac/g/ki/ki03/lande/extended_catalog/monte_carlo/ts_ext/v3_emin_1000/merged.hdf5
    \end{center}
    \caption{Lalla}\label{ts_ext_mc}
  \end{figure}

@@

\clearpage
\begin{sidewaystable}
    \begin{centering}
      \begin{tabular}{rrrrrrrrrrr}
        Name           &    GLON &    GLAT & $\sigma(^\circ)$ &      TS & $\text{TS}_\text{ext}$ & Major & Minor &   Ang & Flux ($10^{-9}$) &         Index \\
        \hline
        \multicolumn{11}{l}{$E > 1\gev$} \\
        \hline
        SMC            & 302.87  &  -44.65 &    $1.59\pm0.15$ &    93.1 &                   51.2 & 0.173 & 0.129 &  41.9 &   $3.0\pm0.4$    & $2.42\pm0.16$ \\
        LMC            & 278.58  &  -32.82 &    $2.26\pm0.09$ &   384.2 &                304.374 & 0.096 & 0.071 & -35.5 &  $12.9\pm0.7$    & $2.42\pm0.08$ \\
        IC443          & 189.05  &  3.04   &    $0.35\pm0.01$ & 10765.3 &                535.282 & 0.006 & 0.006 &  84.0 &  $65.2\pm1.2$    & $2.23\pm0.02$ \\
        W28            & 6.51    &  -0.29  &    $0.39\pm0.02$ &  1231.3 &                   92.1 & 0.014 & 0.013 &  30.4 &  $55.9\pm1.8$    & $2.65\pm0.03$ \\
        W30            & 8.61    &  -0.20  &    $0.36\pm0.04$ &   458.1 &                  66.0  & 0.020 & 0.018 &  14.1 &  $30.0\pm1.8$    & $2.58\pm0.06$ \\
        W44            & 34.68   &  -0.42  &    $0.34\pm0.02$ &  1387.6 &                  111.3 & 0.009 & 0.009 & -39.4 &  $74.7\pm1.0$    & $2.67\pm0.01$ \\
        W51C           & 49.12   &  -0.44  &    $0.28\pm0.02$ &  2174.7 &                   87.6 & 0.010 & 0.010 &  59.4 &  $41.6\pm1.3$    & $2.38\pm0.04$ \\
        \hline
        \multicolumn{11}{l}{$E > 10\gev$} \\
        \hline
        HESS J1825-137 &   17.58 &   -0.46 &    $0.64\pm0.08$ &    85.6 &                   62.5 & 0.050 & 0.045 & 33.6  &     $19.4\pm1.4$ & $2.27\pm0.07$ \\
        MSH 15-52      &  320.39 &   -1.22 &    $0.20\pm0.06$ &    73.7 &                    9.5 & 0.033 & 0.032 & 3.9   &      $4.7\pm0.7$ & $1.88\pm0.12$ \\
      \label{known_extended_sources}
      \end{tabular}
      \caption{The fit results for the known extended sources that
      were found by our analysis. The top results were found using
      an energy range between $1\gev$ and $100\gev$.
      The quoted flux is in units of $10^{-9}\text{ph}/\text{cm}^2/\text{s}$ and 
      is the flux in the fit energy range.
      The lower analysis was done using events between
      $10\gev$ and $100\gev$ and the quoted flux
      values are in the fit energy range. All sources were
      fit using a disk morphology. The localiztaion and extension
      were found using \pointlike while the TS and spectral
      values were calculated using \gtlike.
      The TS value was computed using 
      the assumed disk morphology. The Centaurus A Lobes,
      the Cygnus Loop, and Vela X were not found to be extended by
      this too. The reasons for this are discussed in~\ref{validate_known}.
      }
    \end{centering}
\end{sidewaystable}

@@

\begin{sidewaystable}
    \begin{centering}
      \begin{tabular}{rrrrrrrrrrr}
        Name           &    GLON &    GLAT & $\sigma(^\circ)$ &      TS & $\text{TS}_\text{ext}$ & Major & Minor & Ang & Flux ($10^{-9}$) & Index \\
        \hline
        \multicolumn{11}{l}{$E > 1\gev$} \\
        \hline
        1FGL J1628.6-2419c \\
        1FGL J1554.0-5345c \\
        1FGL J0823.3-4248 \\
        \hline
        \multicolumn{11}{l}{$E > 10\gev$} \\
        \hline
        1FGL J2020.0+4049 \\
        1FGL J1837.5-0659c \\
        1FGL J1632.9-4802c \\
        1FGL J1613.6-5100c \\
        \hline
      \label{new_ext_srcs}
      \end{tabular}
      \caption{}
    \end{centering}
\end{sidewaystable}

>>>>

\usepackage{rotating}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{xspace}

\newcommand{\mev}{\text{MeV}\xspace}
\newcommand{\gev}{\text{GeV}\xspace}
\newcommand{\sr}{\text{sr}\xspace}
\newcommand{\s}{\text{s}\xspace}
\newcommand{\ph}{\text{ph}\xspace}
\newcommand{\cm}{\text{cm}\xspace}
\newcommand{\tsext}{\ensuremath{\text{TS}_\text{ext}}\xspace}
\newcommand{\ts}{\text{TS}\xspace}
\newcommand{\pointlike}{{\em pointlike}\xspace}
\newcommand{\gtlike}{{\em gtlike}\xspace}

@@

On the other hand, since the null hypothesis rests on the edge of
parameter space, when the extension is fixed to 0, Wilk's Theorem does
not formally hold\cite{Warnings about Wilk's Theorem Paper}.  One might
expect the actual distribution to be a half $\chi^2_1$ distribution with
one degree of freedom plus half of a delta function at 0:
\begin{equation}
  P(\ts)=\tfrac{1}{2}(\chi^2_1(\ts)+\delta(\ts)).
\end{equation}
The false detection probability can be estimated by integrating this function 
from an observed test statistic value to infinity. It is for this
particular distribution that the often quoted result holds that
$\sqrt{\ts}$ is a measure of the number of $\sigma$ of the detection.

@@

\section{Monte Carlo Validation}\label{monte_carlo_validation}

@@

Fermi LAT data was simulated using the publically avaliabable Science
Tools package {\em gtobssim}\cite{GTOBSSIM_CITATION}. The sources were
simulated with a powerlaw spectral model with 6 Were given 6 $>100\mev$
fluxes ranging from $3\times 10^{-9} \ph/\cm^2/s$ to 
$10^{-6} \ph/\cm^2/s$.
The sources were then simulated with spectral index ($\gamma$) values of
1.5, 2, 2.5, and 3.  These values were picked to probe a representative
range measurable values.  For particular spectral indices, only the
fluxes which would create a statistically significant source detection
($\ts>25$) where selected, since we are only interested in
testing for extension sources with a significant extent. The sources were
simulated on top of an isotropic powerlaw background with a Sreekumar-like
spectrum ($>100\mev$ flux of 1.5e-5 and spectral index 2.1).\cite{Sreekumar
et al. ApJ 494 pag 523 1998}

The monte carlo simulation was perforormed over a one year time interval using
a default rocking profile and an assumed livetime fraction of 0.8.
The reconstruction was perfromed with events from an energy range of
$1\gev$ to $100\gev$ using 4 energy bins per decade and using the Pass 7 Version 6
source instrument response function (IRFs) to be consistent with the following analysis.

@@

To calculate the LAT's sensitivity to spatially extended sources,
we simulated sources with a uniform radially symmetric
disk morphology on top of a powerlaw
Sreekumar-like isotropic spectrum.\cite{Sreekumar et al. ApJ 494 pag
523 1998}.  For a given extension and spectral index, we calculated the
sensitivity by varying the flux of a source until we found 
when $\tsext=25$. In particular, we hand picked a flux range
where $\tsext<25$ and $\tsext>25$ and simulated 10 points with
a log uniform distribution in this range and performed an extension
test for each of these fluxes. Since the measured signifciance is
a statistical which will vary from realization to realization,
we then repeated this procedure $>15$ times for each spectral
and spatial model.
By fitting a line to the flux vs $\tsext$ data, we were able to
estimage the flux at which $\tsext=25$.

@@

First, we took the spatial and spectral model found using \pointlike
and performed a crosscheck by refitting the spectral parameters using 
\gtlike.
We used a square ROI $10^\circ$ in diamater, the same 4 degrees
per decade, and $0.125^\circ$ energy binning.
The \gtlike analysis provided a second estimate of the spectral
paramters of the extended source as well as a second calculation of
$\ts_\text{disk}$, $\ts_\text{point}$, and 
$\tsext$. We only looked for extended sources which 
both \pointlike and \gtlike considered significantly extended.

@@

To validate our method and assess systematic issues with our
analysis, we used \pointlike to test known active galaxies (AGN) for extension.
\gev emission from AGN is believed to comes from the
core of supermassive blackholes. Since this happens in a very small region
in the core of very distant galaxies,

AGN are not expected to be spatially resolvable and therefore
provide a good calibration source to demonstrate the efficacy of our
tool. Nevertheless, it would be very interesting if AGN could be
spatially resolved AGN and there are theories that predict
this\cite{pair_halo_paper, http://adsabs.harvard.edu/doi/10.1086/187222}.

Following the Fermi-LAT one year catalog, the Fermi collaboration
published a list of the Fermi catalog sources that had a high probability
association with AGN. The first year catalog had 709 AGN associated with
671 distinct 1FGL sources at high latitude ($|b|>10^\circ$).  For our
study, we are looking to assess systematics with extension fitting so
it is important to avoid any possible issues with AGN associations.
For that reason, we select only the 599 AGN which make it into the
``clean'' AGN sample. An AGN association is only considered ``clean''
if it has a high probability of association $P\ge 80\%$, if it is the
only AGN associated with the 1FGL source, and if there are no flags
on the source which shed doubt on the source\cite{1FGL}. These last two
conditions are especially important for our analysis. One might expect
source confusion between two AGN look like a spatially extended source.
Testing only unflagged sources is also important because it removes
any catalog sources coincident with structures in the diffuse emission.
It is possible that these flagged catalog sources which are really poorly
modeled diffuse emission might also look extended.

Of the 599 ``clean'' AGN, we select 556 of these 1FGL sources which
we uniquely associate with a 2 year catalog source. And we furthermore
restrict our select to 515 of these AGN for which we fit $\ts>25$ using
\pointlike.  Our intention here is not to find the largest sample of
AGN and this will be the scope of a follow up AGN association paper. Our
purpose is simply to find a good sample of AGN which can be used to
test the systematics of our tool.

Using the same extension fitting procedure as described above, we test
these 515 AGN for extension. A histogram of the fit \tsext values is
shown in figure~\ref{agn_ts_ext}. Overlaid on the plot is again
a $\chi^2/2$ distribution suggested by Wilk's Theorem.
This plot shows a worse agreement with the theoretical distribution
then was found by our monte carlo study in figure~\ref{ts_ext_mc}.

Several possible systematics could cause this discrepancy. The first
is that in our analysis we fit each source with a powerlaw index.
AGN tend to have curved spectral and fitting with a wrong spectral
model might effect the value of \tsext. Nevertheless, since we use only
events with $E>1\gev$, this would effect is not expected to be large.
Another possible source for the discrepancy is that pointlike performs a
likelihood analysis without modeling the energy dispersion of our source.
But energy dispersion is expected to be more significant at low
energy and furthermore if this was a signifciant effect the same results
would have showed up with the monte carlo simultions which included the
effects of energy dispersion.

The third possible effect causing this discrepancy is an
imperfect modeling of the PSF of the LAT.  Before launch,
the LAT PSF was determined using a Monte Carlo simulation of
the detector.  After launch, a discrepancy was found using flight
data above a few \gev in the PSF measured using very bright AGN.
This result was presented in conference and a publication is in preparation.
Subsequently, the PSF was fit empirically to these bright AGN and
this empirical parameterization is used in the Pass 7 Version 6 IRFs.\cite{
https://confluence.slac.stanford.edu/download/attachments/102860834/FermiSymp2011_CAPSF_v5_ROTH.pptx
}. But our current parameterization is not perfect. There are 
especially lingering issues because there is not good enough statistics
at high energy to validate the PSF as a function of the incident $\theta$
angle of a photon. It is likely that these issues could cause this 
systematic in the fit value of \tsext for point sources. We should
furtheremore note that since the PSF was

with only 2 AGN having $\tsext>10$ and the maximum having $\tsext=13.7$

@@

\begin{table}
  \begin{centering}
\begin{tabular}{ | r | r | r | r | }
\hline
$\gamma$ & flux ($\ph/\cm^2/\s$) & $N_\text{sims}$ & $<\ts>$ \\
\hline
  1.5 &          $10^{-6}$ &           11405 &  90861 \\
      &  $3\times 10^{-7}$ &           11490 &  21922 \\
      &          $10^{-7}$ &           11101 &   5765 \\
      &  $3\times 10^{-8}$ &           10269 &   1262 \\
      &          $10^{-8}$ &            9941 &    306 \\
      &  $3\times 10^{-9}$ &           10427 &     61 \\
\hline
    2 &          $10^{-6}$ &           11632 &  22025 \\
      &  $3\times 10^{-7}$ &           11622 &   4886 \\
      &          $10^{-7}$ &           11115 &   1159 \\
      &  $3\times 10^{-8}$ &           10503 &    222 \\
      &          $10^{-8}$ &            9893 &     50 \\
\hline
  2.5 &          $10^{-6}$ &           11522 &   4722 \\
      &  $3\times 10^{-7}$ &           11445 &    948 \\
      &          $10^{-7}$ &           10966 &    202 \\
      &  $3\times 10^{-8}$ &            8227 &     41 \\
\hline                                                
    3 &          $10^{-6}$ &           11264 &    949 \\
      &  $3\times 10^{-7}$ &           10986 &    172 \\
      &          $10^{-7}$ &            7855 &     40 \\
\hline
\end{tabular}
\caption{
This table presents a list of the spectral models (flux and spectral index)
used in the monte carlo study of 
\pointlike described in section~\ref{monte_carlo_validation}.
For each spectral model, the number of statistically indepdent simulations
and the average test statistic found for that given spectral model
($<\ts>$) is tabulated. 
The important feature to see in this table is that the monte carlo simulation
probes most of the sources parameters that could be detected by the LAT.
The simulation probles a wide range of spectral indices (from index 1.5 to 3) and
a wide range of the fluxes (varying
from a close to $5\sigma$ source detection to a $>10\sigma$ source detection).
Only simluations which produced statistically
significant detections ($\ts>25$) were kept. 
What is quoted is the $>100\mev$ integral flux in measured in units of $\ph/\cm^2/\s$.
}
\label{ts_ext_num_sims}
  \end{centering}
\end{table}

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/ts_ext_emin_1000.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v3/plot.py
    % using data from /nfs/slac/g/ki/ki03/lande/extended_catalog/monte_carlo/ts_ext/v3_emin_1000/merged.hdf5
    \end{center}
    \caption{
    The results of the monte carlo simulation described in section
    \ref{monte_carlo_validation} testing the null distribution of
    the likelihood ratio test for extension.  The $x$ axis of this
    plot is \tsext and the $y$ axis is the cumulative density for
    \tsext that was found by testing simulated point sources of
    various spectral models for extension. The four plots represent
    different spectral indices (for $\gamma$ of 1, 2, 2.5, and 3).
    And the different colors lines represent different fluxes chosen
    to span a representative range of Overlayed on the plot in dashed
    red is the cumulative density function of $\chi^2(\ts)/2$ which is
    suggested by Wilk's theorem as the theoretical distribution these
    curves should should follow.  Overall, it should be noted that there
    is a surprisingly good agreement between the monte carlo study and
    the theoeretical distribution. And for most spectral parameters, the
    Monte Carlo curve lies to the left of the theoretical curve, which
    would imply that using Wilk's Theorem as the null distribution would
    conservativly underestimate the signifcance of a source detection. In
    the rest of the paper, we use this theoretical curve to estimate
    the significance of our source detections.  What is quoted is the
    $>100\mev$ integral flux in measured in units of $\ph/\cm^2/\s$.
    For each spectral model, more information about the simulations is
    summarized in table~\ref{ts_ext_num_sims}.
    }\label{ts_ext_mc}
  \end{figure}

@@

\clearpage
\begin{sidewaystable}
    \begin{centering}
      \begin{tabular}{rrrrrrrrrrr}
        Name           &    GLON &    GLAT & $\sigma(^\circ)$ &     \ts & $\tsext$ & Major & Minor &   Ang & Flux ($10^{-9}$) &         Index \\
        \hline
        \multicolumn{11}{l}{$E > 1\gev$} \\
        \hline
        SMC            & 302.87  &  -44.65 &    $1.59\pm0.15$ &    93.1 &                   51.2 & 0.173 & 0.129 &  41.9 &   $3.0\pm0.4$    & $2.42\pm0.16$ \\
        LMC            & 278.58  &  -32.82 &    $2.26\pm0.09$ &   384.2 &                304.374 & 0.096 & 0.071 & -35.5 &  $12.9\pm0.7$    & $2.42\pm0.08$ \\
        IC443          & 189.05  &  3.04   &    $0.35\pm0.01$ & 10765.3 &                535.282 & 0.006 & 0.006 &  84.0 &  $65.2\pm1.2$    & $2.23\pm0.02$ \\
        W28            & 6.51    &  -0.29  &    $0.39\pm0.02$ &  1231.3 &                   92.1 & 0.014 & 0.013 &  30.4 &  $55.9\pm1.8$    & $2.65\pm0.03$ \\
        W30            & 8.61    &  -0.20  &    $0.36\pm0.04$ &   458.1 &                  66.0  & 0.020 & 0.018 &  14.1 &  $30.0\pm1.8$    & $2.58\pm0.06$ \\
        W44            & 34.68   &  -0.42  &    $0.34\pm0.02$ &  1387.6 &                  111.3 & 0.009 & 0.009 & -39.4 &  $74.7\pm1.0$    & $2.67\pm0.01$ \\
        W51C           & 49.12   &  -0.44  &    $0.28\pm0.02$ &  2174.7 &                   87.6 & 0.010 & 0.010 &  59.4 &  $41.6\pm1.3$    & $2.38\pm0.04$ \\
        \hline
        \multicolumn{11}{l}{$E > 10\gev$} \\
        \hline
        HESS J1825-137 &   17.58 &   -0.46 &    $0.64\pm0.08$ &    85.6 &                   62.5 & 0.050 & 0.045 & 33.6  &     $19.4\pm1.4$ & $2.27\pm0.07$ \\
        MSH 15-52      &  320.39 &   -1.22 &    $0.20\pm0.06$ &    73.7 &                    9.5 & 0.033 & 0.032 & 3.9   &      $4.7\pm0.7$ & $1.88\pm0.12$ \\
      \label{known_extended_sources}
      \end{tabular}
      \caption{The fit results for the known extended sources that
      were found by our analysis. The top results were found using
      an energy range between $1\gev$ and $100\gev$.
      The quoted flux is in units of $10^{-9}\ph/\cm^2/\s$ and 
      is the flux in the fit energy range.
      The lower analysis was done using events between
      $10\gev$ and $100\gev$ and the quoted flux
      values are in the fit energy range. All sources were
      fit using a disk morphology. The localiztaion and extension
      were found using \pointlike while the TS and spectral
      values were calculated using \gtlike.
      The TS value was computed using 
      the assumed disk morphology. The Centaurus A Lobes,
      the Cygnus Loop, and Vela X were not found to be extended by
      this too. The reasons for this are discussed in~\ref{validate_known}.
      }
    \end{centering}
\end{sidewaystable}

@@

\begin{sidewaystable}
    \begin{centering}
      \begin{tabular}{rrrrrrrrrrr}
        Name           &    GLON &    GLAT & $\sigma(^\circ)$ &      TS & $\tsext$ & Major & Minor & Ang & Flux ($10^{-9}$) & Index \\
        \hline
        \multicolumn{11}{l}{$E > 1\gev$} \\
        \hline
        1FGL J1628.6-2419c \\
        1FGL J1554.0-5345c \\
        1FGL J0823.3-4248 \\
        \hline
        \multicolumn{11}{l}{$E > 10\gev$} \\
        \hline
        1FGL J2020.0+4049 \\
        1FGL J1837.5-0659c \\
        1FGL J1632.9-4802c \\
        1FGL J1613.6-5100c \\
        \hline
      \label{new_ext_srcs}
      \end{tabular}
      \caption{}
    \end{centering}
\end{sidewaystable}
